\plaintitle

### 2016-07-26 drafts/labor/introduction.tex
mondays

\section{Introduction}
% each sentence feels like a thought that's unrelated to the next one
The past decade has seen a proliferation in on--demand work
where workers' statuses are so fleeting that 
they have been described as ``transient''.
After identifying that myriad tasks 
--- from the mundane to the complex ---
can be accomplished
% beginning with ``information work'' such as on
% Amazon Mechanical Turk (AMT).
% ??? ->
% Stemming from the recognition that
% complex tasks might be achievable
% --- and indeed trivial ---
by directing and managing the ``crowd'',
the research and and industry communities have flocked to sites of labor
like Amazon's Mechanical Turk (AMT)
to solicit workers.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using these workers (``Turkers'')
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

>>>>

\section{Introduction}
% each sentence feels like a thought that's unrelated to the next one
The past decade has seen a flourishing of on--demand work
where the statuses of workers have become so fleeting that 
these workers
(known colloquially as ``Turkers'')
have been described as ``transient''
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
% After identifying
The realization
that myriad tasks
--- from the mundane to the complex ---
can be accomplished
by directing and managing this crowd of workers,
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, anonymous labor force.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using Turkers
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.
